\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage{graphics}
\usepackage{/ocean/sallen/allen/bibtex/squashsyllabus}
\textheight10in

\newenvironment{absolutelynopagebreak}
  {\par\nobreak\vfil\penalty0\vfilneg
   \vtop\bgroup}
  {\par\xdef\tpd{\the\prevdepth}\egroup
   \prevdepth=\tpd}


\begin{document}

\section*{Undergraduate Numerical Techniques for Atmosphere, Ocean and Earth Scientists: ATSC 409}
\subsection*{\center\today}

\subsection*{Calendar Entry}

Web-based introduction to the practical numerical solution of ordinary and partial differential equations including considerations of stability and accuracy.  Credit will not be granted for both ATSC 409 and ATSC 506/EOSC 511.

\subsection*{Course Purpose}

The students completing this course will be able to apply standard numerical solution techniques to the solution of problems such as waves, advection, population growth.

\subsection*{Instructors}

       Phil Austin, 2-2175, paustin@eos.ubc.ca, Rm 157 EOS South \\
       Susan Allen, 2-2828, sallen@eos.ubc.ca, Rm 3017 ESB


\subsection*{Prerequisites}

Solution of Ordinary Differential Equations (MATH 215 or equivalent)  AND a programming course.  Partial Differential Equations (Math 316 or Phys 312) is recommended.\footnote{If you have PDE's Lab 7 is strongly recommended, whereas if you do not have PDE's do Lab 6}

\subsection*{Course Structure}

This course is not lecture based. The course is an interactive, computer based laboratory course. The computer will lead you through the laboratory (like a set of lab notes) and you will answer problems most of which use the computer. The course consists of three parts. A set of  interactive, computer based
laboratory exercises, two mini-projects and a final project.

During the meeting times, we will hold short quizzes (just to make sure you are keeping up) and brief presentations to help with technical matters and the more difficult sections of the course.

You can use a web-browser to examine the
course exercises. Point your browser to: 

http://clouds.eos.ubc.ca/$\sim$phil/numeric


\subsection*{Grades}

\begin{itemize}
\item       Laboratory Exercises 30\% 
\item	    Quizzes 10\%
\item 	    Mini-projects 20\%
\item       Project Proposal 5\%
\item       Project 30\% 
\item	    Project Oral Presentation 5\%
\end{itemize}

\subsection*{Meeting Times}

1400-1600 Thursdays, Room 203, Earth and Oceans Sciences (EOS) Main


\subsection*{Laboratory Problem Sets}

The laboratory problem sets can be given to either instructor when completed.
(We have mail boxes in the Earth and Ocean Sciences Main Office).
They may be hand written or typed.  You may wish or be asked to include
plots and diagrams.  You can email us plots instead of printing them.
Sometimes, rather than a large series of plots, you
may wish to include a summarizing table.  If you do not
understand the scope of a problem, please ask.  The time scales given
in the Contents section are based on 7 hours/week additional to class time.  
Help with the labs
is available 1) through a mailing list so you can contact your classmates
and ask them 2) during the weekly scheduled lab or 3) directly from the
instructors.  Assignments, mini-projects and the project are expected on
time.  Late ones will be marked and then the mark will be multiplied by
$(0.9)^{\rm (number\ of\ days\ or\ part\ days\ late)}$.
(Below we give two dates
for each assignment.  You should aim for the first one (this would keep you
totally up to date).  The later one allows a couple of days in case.
)


\subsection*{Contents}

Each laboratory is separated into sessions of about 2 hours.  You may do the 
sessions any time during the week.  You will need to complete three sessions
a week to keep up with the course material covered in the quizzes.

\begin{itemize}
\item Introductory Meeting
\item Laboratory One
\begin{itemize}
\item Four sessions: 1) section 3, 2) section 4, 3) section 5, 4) section 6.
\item Quiz \#1 Objectives\footnote{Objectives is an older term for Learning Goals} pertaining to Lab 1 sections 3-5
\item Quiz \#2 Objectives pertaining to Lab 1 and Lab 2 sections 3-4.
\item Assignment: See web.
\end{itemize}
\item Laboratory Two
\begin{itemize} 
\item Three sessions: 1) section 3-4.1.1, 2) section 4.1.2-end 4, 3) sections 5-7
\item Quiz \#2 Objectives pertaining to Lab 1 and Lab 2 sections 3-4.
\item Quiz \#3 Objectives pertaining to Lab 2 and Lab 3 section 2.
\item Assignment: See web.
\end{itemize} 
\item Laboratory Three
\begin{itemize}
\item Four sessions: 1) section 2- begin 2.4.1, 2) section 2.4.1-end 2, 3) section 3-4, 4) section 5
\item Quiz \#3 Objectives pertaining to Lab 2 and Lab 3 section 2.
\item Quiz \#4 Objectives pertaining to Lab 3.
\item Assignment: See web.
\end{itemize}
\item Mini-Project \#1
\begin{itemize}
\item Two sessions
\item Details on web.
\end{itemize}
\item Laboratory Four
\begin{itemize}
\item Four sessions: 1) section 3, 2) section 4.1-4.2, 3) section 4.3-5, 4) finish problem set
\item Quiz \#5 Objectives pertaining to Lab 4 sections 3-4.2
\item Quiz \#6 Objectives pertaining to Lab 4 and Lab 5 section 3
\item Assignment: See web.
\end{itemize}
\item Laboratory Five
\begin{itemize}
\item Three sessions: 1) section 3, 2) section 4, 3) section 5
\item Quiz \#6 Objectives pertaining to Lab 4 and Lab 5 section 3
\item Quiz \#7 Objectives pertaining to Lab 5
\item Assignment: 4a, 4b, 6-1, 6-2, 6-3
\end{itemize}
\item Mini-Project \#2
\begin{itemize}
\item Two sessions
\item Details on web.
\end{itemize}
\item Laboratory Seven (do 7 if you have PDE's)
\begin{itemize}
\item Four sessions: 1) section 3-4.3, 2) section 4.4-4.5, 3) section 5, 4) section 6
\item Quiz \#8 Objectives pertaining to Lab 7 section 3-4.3
\item Assignment: See web.
\end{itemize}
\item Laboratory Six (do 6 if you do not have PDE's)
\begin{itemize}
\item Four sessions: 1) section 3 2) section 4-4.2 3) section 4.3-4.4, 4) section 5-6
\item Quiz \#8 Objections pertaining to Lab 6 section 3
\end{itemize}
\item Assignment: See web.
\end{itemize}
\clearpage
\begin{absolutelynopagebreak}
\begin{itemize}
\item Project
\begin{itemize}
\item Eight Sessions
\item 20 minute presentation to the class
\item Project report
\end{itemize}
\end{itemize}

\include{schedule}
\end{absolutelynopagebreak}

\end{document}
